Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-12-01 files/Overview.tex
spelling mistake and a word counter python app

Finally the concept of modal analysis is introduced, which is fundamental to this dissertation. First idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam. Then the general case is discussed that follows the article \cite{CVV18}. Given a general vibration problem, it is split into two problems by introducing a trial solution. It can then be verified that these two problems are the eigenvalue problem and an ordinary differential equation. An additional assumption (additional to the assumptions of \cite{VV02}) is introduced by \cite{CVV18}. Under this assumption, the eigenvalue problem has a complete orthonormal sequence of eigensolutions. The solution of the general vibration problem is an infinite series of modal solutions. This formal series solution is then shown to also be valid for a initial value problem. This general case is also applicable to all the models in this dissertation.

@@

In the first part, the authors of \cite{BV13} consider the general vibration problem that is studied in Chapter 2. The general vibration problem has a solution as shown in Chapter 2. The Galerkin Approximation is derived from the general vibration problem and is rewritten into a system of ordinary differential using the Finite Element Method. This oridinary differential equation can be proven to have a unique solution. The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem. The approach of the authors is to calculate the error estimates.

The second part of the chapter considers work done in a textbook \cite{SF73} on eigenvalue problems for elliptic partial differential equations. The specific work discussed, covers the convergence of the eigenvalues and eigenfunctions of a general vibration problem when applying the Finite Element Method. The authors consider a general eigenvalue problem. Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{OR97}, the main result is proven. The specific work done in this section is updating the notation of the textbook, as well as expanding some proofs so that the results are easier to understand.

@@

\subsubsection{Finite element method}
This chapter is preperation for the final chapter in this dissertation. The finite element method is applied to the models of this dissertation. Specifically, it is applied to the Cantilever model problem of the three-dimensional and two-dimensional elastic bosies, as well as the cantilever plate model. The cantilever Timoshenko beam model is excluded since chapter 4 provides an exact method to calculate the eigenvalues and eigenfunctions. Each of the models are assumed to have a rectangular cross-section and is made of the same isotropic material. For each model, a reference configuration is defined. The Galerkin approximation can then be derived and using the Finite Element Method, a system of oridinary differential equations can be obatined. At this point is it easy to derive a eigenvalue problem for each of the models. This eigenvalue problem can be solved using numerical methods.

>>>>

Finally the concept of modal analysis is introduced, which is fundamental to this dissertation. First idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam. Then the general case is discussed that follows the article \cite{CVV18}. Given a general vibration problem, it is split into two problems by introducing a trial solution. It can then be verified that these two problems are the eigenvalue problem and an ordinary differential equation. An additional assumption (additional to the assumptions of \cite{VV02}) is introduced by \cite{CVV18}. Under this assumption, the eigenvalue problem has a complete orthonormal sequence of eigen-solutions. The solution of the general vibration problem is an infinite series of modal solutions. This formal series solution is then shown to also be valid for a initial value problem. This general case is also applicable to all the models in this dissertation.

@@

In the first part, the authors of \cite{BV13} consider the general vibration problem that is studied in Chapter 2. The general vibration problem has a solution as shown in Chapter 2. The Galerkin Approximation is derived from the general vibration problem and is rewritten into a system of ordinary differential using the Finite Element Method. This ordinary differential equation can be proven to have a unique solution. The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem. The approach of the authors is to calculate the error estimates.

The second part of the chapter considers work done in a textbook \cite{SF73} on eigenvalue problems for elliptic partial differential equations. The specific work discussed, covers the convergence of the eigenvalues and eigenfunctions of a general vibration problem when applying the Finite Element Method. The authors consider a general eigenvalue problem. Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{OR76}, the main result is proven. The specific work done in this section is updating the notation of the textbook, as well as expanding some proofs so that the results are easier to understand.

@@

\subsubsection{Finite element method}
This chapter is preperation for the final chapter in this dissertation. The finite element method is applied to the models of this dissertation. Specifically, it is applied to the Cantilever model problem of the three-dimensional and two-dimensional elastic bosies, as well as the cantilever plate model. The cantilever Timoshenko beam model is excluded since chapter 4 provides an exact method to calculate the eigenvalues and eigenfunctions. Each of the models are assumed to have a rectangular cross-section and is made of the same isotropic material. For each model, a reference configuration is defined. The Galerkin approximation can then be derived and using the Finite Element Method, a system of ordinary differential equations can be obtained. At this point is it easy to derive a eigenvalue problem for each of the models. This eigenvalue problem can be solved using numerical methods.
